---
title: |
  Supplementary Material
subtitle: |
  *Acoustic drivers of infant attention in infant-directed speech* [Stage 1 Registered Report]

author:
  - "Juan David Leongómez\\textsuperscript{1*} \\orcidlink{0000-0002-0092-6298}"
  - "Milena Vásquez-Amézquita\\textsuperscript{1} \\orcidlink{0000-0001-7317-8430}"
  - "David A. Puts\\textsuperscript{2} \\orcidlink{0000-0002-6478-1980}"

date: today
date-format: "D MMMM YYYY"

format:
  pdf:
    documentclass: article
    cite-method: biblatex
    biblio-style: apa
    number-sections: true
    tbl-prefix: "S"
    fig-prefix: "S"
    toc: true
    toc-depth: 3
    toc-title: "Table of Contents"
    geometry: "margin=2.5cm"
    fontsize: 11pt
    colorlinks: true
    linkcolor: "gray"
    citecolor: "gray"
    urlcolor: "blue"
    keep-tex: false
    include-in-header:
      text: |
        \usepackage{tabularray}
        \usepackage{ninecolors}
        \usepackage{float}
        \floatplacement{figure}{H}
        \floatplacement{table}{H}
        \usepackage{fancyhdr}
        \pagestyle{fancy}
        \lhead{Leongómez et al.}
        \rhead{Supplementary Material --- IDS Attentional Drivers (Stage 1 RR)}
        \setlength{\headheight}{15pt}
        \usepackage{caption}
        \DeclareCaptionLabelFormat{suppfig}{Figure S#2}
        \DeclareCaptionLabelFormat{supptbl}{Table S#2}
        \captionsetup[figure]{labelformat=suppfig, labelfont=bf, labelsep=period, skip=5pt}
        \captionsetup[table]{labelformat=supptbl, labelfont=bf, labelsep=period, skip=5pt}
        \usepackage{multirow}
        \usepackage{setspace}
        \usepackage{orcidlink}
        \usepackage{hyperref}
        \let\oldmaketitle\maketitle
        \renewcommand{\maketitle}{%
          \oldmaketitle
          \begin{flushleft}
          \small
          \textsuperscript{1} CODEC: Cognitive and Behavioural Sciences Research Group,
          Faculty of Psychology, Universidad El Bosque, Bogot\'{a} 110121, Colombia\\[0.4em]
          \textsuperscript{2} Departments of Anthropology and Psychology,
          Pennsylvania State University, University Park, PA 16802, USA\\[0.4em]
          \textsuperscript{*} Correspondence:
          \href{mailto:jleongomez@unbosque.edu.co}{jleongomez@unbosque.edu.co}
          \end{flushleft}
          \vspace{0.5em}
        }
        \AtBeginBibliography{\addcontentsline{toc}{section}{References}}
        \ExecuteBibliographyOptions{doi=true}
        \AtEveryBibitem{
          \iffieldundef{doi}{}{\clearfield{url}}
          \clearfield{month}
          \clearfield{day}
          \clearfield{issn}
          \clearfield{isbn}
        } 

bibliography: Files/Bibliography.bib
link-citations: true

execute:
  echo: true
  warning: false
  message: false
  cache: true

knitr:
  opts_chunk:
    fig.pos: "H"
    fig.width: 10
    fig.height: 6
    out.width: "100%"
---

\newpage

\colorbox{BurntOrange}{CHECK MISSING URLs}

# Overview {.unnumbered}

This document is the supplementary material for the registered report *Acoustic drivers of infant attention in infant-directed speech*. It covers two topics: stimulus preparation and design, including the derivation of population norms for acoustic manipulation and the counterbalancing scheme; and a simulation-based power analysis. The study uses a 2×2×2 fully crossed within-subjects design to examine the effects of three independently manipulated acoustic properties of infant-directed speech (IDS) on total fixation time (ms) in pre-linguistic infants aged 3–9 months: mean fundamental frequency ($f_0$ mean) and pitch variability ($f_0$ SD) are the two confirmatory parameters (H1 and H2), and formant frequencies (proportional scaling of all formant frequencies, targeting apparent vocal tract length) are treated as an exploratory parameter.

The primary statistical model is a linear mixed model (LMM):

$$\texttt{fixation\_time} \sim f_0\text{ SD} \times f_0\text{ mean} \times \texttt{formant} + \texttt{block} + \texttt{avatar} + (1 + \texttt{avatar} \mid\mid \text{ID}) + (1 \mid \text{original})$$

The simulation uses a simplified version of this model ($\texttt{fixation\_time} \sim f_0\text{ SD} \times f_0\text{ mean} \times \texttt{formant} + (1 \mid \text{ID})$) which omits the additional fixed and random effects. This simplification is conservative for the reasons described at the end of this section.

Three complementary analyses are presented here:

1. **Frequentist detection power** (Monte Carlo, H$_1$ population): the probability of detecting each main effect via a significant $p$-value ($\alpha = .05$) in the LMM ANOVA, as a function of sample size. Estimated from a superpopulation incorporating all expected effects.

2. **Frequentist equivalence power** (Monte Carlo, H$_0$ population): the probability of concluding practical equivalence with zero (i.e., the probability that a 90% CI from the marginal `emmeans` contrast falls entirely within pre-specified equivalence bounds of ±150 ms) as a function of sample size. Critically, this is estimated from a **separate** superpopulation in which all acoustic effects are set to zero, because using the H$_1$ data would yield near-zero equivalence rates by design (the CI stays outside the bounds precisely because real effects exist).

3. **Bayesian sensitivity analysis** (brms + ROPE): a number of Bayesian LMMs fitted in `brms` at the target sample size ($n = 200$) under each population. The proportion of the posterior for each main effect falling within the Region of Practical Equivalence (ROPE: ±150 ms) is computed using `bayestestR::equivalence_test()`, serving as a secondary robustness check.

The simulation assumes one observation per condition per participant and a single stimulus source. The actual design includes two blocks, yielding two observations per condition per participant, which halves the variance of each `emmeans` contrast, reducing the SE by a factor of approximately $\sqrt{2}$ relative to the simulated design. The simulation additionally omits random effects for original voice recordings $(1 \mid \text{original})$ and the by-participant avatar slope $(1 + \texttt{avatar} \mid\mid \text{ID})$, which introduce additional variance not captured here. The net power estimates are therefore conservative: the doubling of within-participant observations substantially outweighs the additional variance from the expanded random-effects structure, and the reported power curves should be treated as lower bounds on the power of the actual design.

**Reproducibility.** All code, seeds, and parameters are documented here. The complete source file is available at: \colorbox{BurntOrange}{https://github.com/JDLeongomez/Proyecto-IDS}

\newpage

# Stimuli and Design

## Stimulus Counterbalancing

The table below shows the assignment of acoustic conditions to original recordings (A--D) and avatars across the four counterbalancing lists (G1--G4) and two blocks. Within each block, every original appears exactly twice, paired with different acoustic conditions. Across lists, each acoustic condition is paired equally often with each original. Block 2 mirrors Block 1 with avatars swapped, fully counterbalancing avatar at the within-participant level.

```{r}
#| label: tbl-design
#| tbl-cap: "Assignment of acoustic conditions to original recordings and avatars across counterbalancing lists and blocks."
#| echo: false

design_tbl <- data.frame(
  `$f_0$ SD`        = rep(c("Low","Low","Low","Low","High","High","High","High"), 2),
  `$f_0$ mean`      = rep(c("Low","Low","High","High","Low","Low","High","High"), 2),
  `Formant freq.`   = rep(c("Low","High","Low","High","Low","High","Low","High"), 2),
  G1 = c("A (Duck)","B (Bear)","C (Duck)","D (Bear)",
          "A (Bear)","B (Duck)","C (Bear)","D (Duck)",
          "A (Bear)","B (Duck)","C (Bear)","D (Duck)",
          "A (Duck)","B (Bear)","C (Duck)","D (Bear)"),
  G2 = c("B (Bear)","C (Duck)","D (Bear)","A (Duck)",
          "C (Duck)","D (Bear)","A (Duck)","B (Bear)",
          "B (Duck)","C (Bear)","D (Duck)","A (Bear)",
          "C (Bear)","D (Duck)","A (Bear)","B (Duck)"),
  G3 = c("C (Duck)","D (Duck)","A (Bear)","B (Bear)",
          "D (Bear)","A (Bear)","B (Duck)","C (Duck)",
          "C (Bear)","D (Bear)","A (Duck)","B (Duck)",
          "D (Duck)","A (Duck)","B (Bear)","C (Bear)"),
  G4 = c("D (Bear)","A (Bear)","B (Duck)","C (Duck)",
          "B (Duck)","C (Duck)","D (Bear)","A (Bear)",
          "D (Duck)","A (Duck)","B (Bear)","C (Bear)",
          "B (Bear)","C (Bear)","D (Duck)","A (Duck)"),
  check.names = FALSE
)

tt(design_tbl) |>
  group_tt(
    i = list("Block 1" = 1, "Block 2" = 9)
    ) |>
  style_tt(
    i = c(1, 10), bold = TRUE
    ) |>
  style_tt(
    j = 3, i = c(0, 2:9, 11:18), line = "r"
    ) |> 
  style_tt(align = "c") |>
  format_tt(escape = FALSE)
```

## Stimulus Generation

Eight manipulated versions of each original IDS recording will be generated using a custom Praat script [@praat] (available at the project repository). Each version corresponds to one cell of the fully crossed 2×2×2 design, in which mean fundamental frequency ($f_0$ mean), pitch variability ($f_0$ SD), and formant frequencies are each set to a High or Low level.

The two levels for each parameter are defined as ±1 between-speaker standard deviation (SD) from the IDS population distribution, computed from Hilton et al.'s [-@hilton2022] cross-cultural corpus of female IDS ($n = 21$ societies; audio: <https://doi.org/10.5281/zenodo.5525161>). Using a single large cross-cultural dataset as the sole source of population norms follows the approach of Aung et al. [-@aung2024], who used ERB-unit steps calibrated to population norms for cross-cultural voice manipulation. The manipulation targets for each speaker are:

$$\text{target}_{\text{high}} = \text{baseline}_{\text{speaker}} + \text{SD}_{\text{population}}, \quad \text{target}_{\text{low}} = \text{baseline}_{\text{speaker}} - \text{SD}_{\text{population}}$$

The resulting offsets are:

- **$f_0$ mean:** $\pm 51$ Hz ($1 \times 50.8$ Hz; between-speaker SD from Hilton et al. [-@hilton2022], population mean $f_0 = 261.8$ Hz). Cross-checked against Cox et al. [-@cox2023] (meta-analytic OSF data, $n = 202$ female speakers; SD = 40.1 Hz), whose smaller value is consistent with the lower cross-cultural diversity of that dataset.
- **$f_0$ SD:** $\pm 28$ Hz ($1 \times 28.4$ Hz; between-speaker SD from Hilton et al. [-@hilton2022], population mean $f_0$ SD = 66.6 Hz). Cross-checked against Broesch and Bryant [-@broesch2015] (Table 1; Western SD = 24.0 Hz, non-Western SD = 22.4 Hz), both consistent with the Hilton et al. value.
- **Formant frequencies:** $\pm 4.6\%$ proportional scaling ($1 \times$ CV = 0.046). F1–F4 were extracted from the Hilton et al. [-@hilton2022] corpus audio using a custom Praat script; the between-speaker SD of the geometric mean of F1–F4 was 87.4 Hz on a population mean of 1920.9 Hz (CV = 0.046). This replaces a provisional pilot estimate and provides a principled population anchor for the formant manipulation; however, formant frequencies remain exploratory for the reasons detailed in the main manuscript (sparse literature on infant attentional responses to this parameter; detection power below the 95% confirmatory threshold).

An initial pilot using a manipulation of $\pm 1.5$ SD produced pronounced PSOLA artefacts (octave jumps, mechanical quality) across all $f_0$ conditions. Reducing the manipulation to $\pm 1$ SD yielded perceptually natural stimuli; this is therefore an empirical constraint on the manipulation magnitude, not a theoretical preference.

### Population norms

The between-speaker population SDs used to calibrate the manipulation targets were derived from Hilton et al.'s [-@hilton2022] corpus [@hilton2022corpus]. Their GitHub repository provides per-recording acoustic measures (including $f_0$ mean and $f_0$ SD) but does not include F3 or F4. To compute the geometric mean of F1--F4 (used as the vocal tract length proxy), F1--F4 were re-extracted from the edited audio files using a custom Praat script. The analysis and all outputs are archived in the `population_norms/` subfolder of this supplementary.

**Step 1: Formant extraction.** The IDS files (vocalization type `B`, $n = 458$) were downloaded from Zenodo [@hilton2022corpus] and filtered to female speakers using the `stimuli-info.csv` metadata file (column `Gender == "F"`). F1--F4 were extracted with the following Praat script, using the same Burg [analysis settings](https://github.com/themusiclab/infant-speech-song/blob/main/analysis/acoustics_processing/3_masterscript.praat) as Hilton et al. (5500 Hz ceiling, five formants, 25 ms window):

```{r}
#| label: praat-extract-display
#| echo: false
#| eval: true
#| results: 'asis'

lines <- readLines("population_norms/extract_formants_IDS.praat")
cat("```praat\n", paste(lines, collapse = "\n"), "\n```\n", sep = "")
```

**Step 2: Population norm derivation.** The extracted formant data were joined with the Hilton et al. acoustic CSV and speaker metadata, filtered to female IDS speakers, and aggregated to one row per speaker before computing between-speaker SDs.

```{r}
#| label: pop-norms-load
#| echo: false
#| cache: false

library(tinytable)
library(tidyverse)
library(readr)

by_speaker <- read_csv("population_norms/by_speaker.csv", show_col_types = FALSE)

norms <- by_speaker |>
  summarise(
    n_speakers      = n(),
    f0mean_pop_mean = mean(f0_mean_hz,    na.rm = TRUE),
    f0mean_pop_sd   = sd(f0_mean_hz,      na.rm = TRUE),
    f0mean_target   = sd(f0_mean_hz,      na.rm = TRUE),
    f0sd_pop_mean   = mean(f0_sd_hz,      na.rm = TRUE),
    f0sd_pop_sd     = sd(f0_sd_hz,        na.rm = TRUE),
    f0sd_target     = sd(f0_sd_hz,        na.rm = TRUE),
    vtl_pop_mean    = mean(vtl_proxy_hz,  na.rm = TRUE),
    vtl_pop_sd      = sd(vtl_proxy_hz,    na.rm = TRUE),
    vtl_cv          = sd(vtl_proxy_hz,    na.rm = TRUE) / mean(vtl_proxy_hz, na.rm = TRUE),
    vtl_target_pct  = sd(vtl_proxy_hz,    na.rm = TRUE) / mean(vtl_proxy_hz, na.rm = TRUE)
  )
```

```{r}
#| label: pop-norms-code
#| echo: true
#| eval: false
#| code-summary: "hilton2022_population_norms.R (display only — precomputed)"

# Full analysis code is in population_norms/hilton2022_population_norms.R
# Precomputed outputs loaded from population_norms/by_speaker.rds and norms.rds
readLines("population_norms/hilton2022_population_norms.R") |> cat(sep = "\n")
```

@fig-norms-dist shows the between-speaker distributions for all three parameters. The derived manipulation targets are summarised in @tbl-norms, together with cross-checks from Cox et al. [-@cox2023] and Broesch and Bryant [-@broesch2015].

```{r}
#| label: fig-norms-dist
#| fig-cap: "Between-speaker distributions of the three acoustic parameters in female
#|   infant-directed speech, derived from Hilton et al. (2022). Vertical dashed lines
#|   show population means; shaded bands show ±1 SD (the manipulation targets)."
#| fig-width: 9
#| fig-height: 3.2
#| echo: false
#| eval: true
#| cache: false

# Use case_match (robust in dplyr >= 1.1) and plain text labels (no label_parsed)
plot_data <- by_speaker |>
  select(f0_mean_hz, f0_sd_hz, vtl_proxy_hz) |>
  pivot_longer(everything(), names_to = "parameter", values_to = "value") |>
  mutate(
    parameter = case_match(
      parameter,
      "f0_mean_hz"   ~ "f0 mean (Hz)",
      "f0_sd_hz"     ~ "f0 SD (Hz)",
      "vtl_proxy_hz" ~ "Formant freq. — geom. mean F1\u2013F4 (Hz)"
    ),
    parameter = factor(parameter, levels = c(
      "f0 mean (Hz)", "f0 SD (Hz)", "Formant freq. — geom. mean F1\u2013F4 (Hz)"
    ))
  ) |>
  group_by(parameter) |>
  mutate(pmean = mean(value, na.rm = TRUE),
         psd   = sd(value,   na.rm = TRUE)) |>
  ungroup()

ggplot(plot_data, aes(x = value)) +
  geom_rect(aes(xmin = pmean - psd, xmax = pmean + psd,
                ymin = -Inf, ymax = Inf),
            fill = "lightgrey", alpha = 0.08, colour = NA) +
  geom_histogram(bins = 20, fill = "steelblue", colour = "white", alpha = 0.85) +
  geom_vline(aes(xintercept = pmean), linetype = "dashed", linewidth = 0.6) +
  facet_wrap(~ parameter, scales = "free") +
  labs(x = NULL, y = "Number of speakers") +
  theme_minimal(base_size = 10)
```

```{r}
#| label: tbl-norms
#| tbl-cap: "Population norms for the three acoustic parameters derived from female
#|   IDS speakers in Hilton et al. (2022), and cross-checks from independent
#|   sources. All manipulation targets are set at ±1 between-speaker SD. The formant
#|   frequencies target is a proportional scaling factor (CV × 1)."
#| echo: false
#| eval: true

norms_tbl <- tibble(
  Parameter = c("$f_0$ mean", "$f_0$ SD", "Formant freq."),
  `Pop. mean` = c(
    paste0(round(norms$f0mean_pop_mean, 1), " Hz"),
    paste0(round(norms$f0sd_pop_mean,   1), " Hz"),
    paste0(round(norms$vtl_pop_mean,    1), " Hz")
  ),
  `Pop. SD` = c(
    paste0(round(norms$f0mean_pop_sd, 1), " Hz"),
    paste0(round(norms$f0sd_pop_sd,   1), " Hz"),
    paste0(round(norms$vtl_pop_sd,    1), " Hz")
  ),
  `Target ($\\pm$1 SD)` = c(
    paste0("$\\pm$", round(norms$f0mean_target, 0), " Hz"),
    paste0("$\\pm$", round(norms$f0sd_target,   0), " Hz"),
    paste0("$\\pm$", round(norms$vtl_target_pct * 100, 1), "\\%")
  ),
  `Cross-check` = c(
    "$^a$",
    "$^b$",
    "---"
  )
)

tt(norms_tbl,
   width = 1,
   notes = list(
     a = "\\cite{cox2023}, meta-analytic OSF data; n = 202 female speakers; SD = 40.1 Hz.",
     b = "\\cite{broesch2015}, Table 1; Western SD = 24.0 Hz, non-Western SD = 22.4 Hz."
   )
) |>
  style_tt(align = "lcccc") |>
  format_tt(escape = FALSE)
```

Baseline $f_0$ mean and $f_0$ SD are estimated from each recording using Praat's autocorrelation-based pitch analysis; formant frequencies are estimated using Burg's method with a 5500 Hz analysis ceiling, consistent with the synthesis ceiling. Manipulation proceeds in two sequential steps per stimulus.

**Step 1 — Formant frequencies.** Formant frequencies are manipulated first, applied directly to the original (unmodified) recording, via an LPC source-filter resynthesis pipeline adapted from the Praat Vocal Toolkit [@corretge2012]. The manipulation proportionally scales all formant frequencies by the target ratio $r = 1 \pm k_{\text{formant}}$, thereby shifting apparent vocal tract length while leaving the pitch contour unchanged. Briefly: (a) the spectral content above the analysis ceiling (5500 Hz for female speakers) is preserved as a high-frequency residual; (b) the recording is resampled to twice the analysis ceiling; (c) a robust formant analysis is performed and converted to an LPC filter; (d) the signal is inverse-filtered to isolate the glottal source; (e) all formant frequencies in a copy of the formant object are scaled by $r$; (f) the modified formant object is converted to a new LPC filter and used to re-filter the source; (g) the result is resampled to the original rate and the high-frequency residual is added back. Because this pipeline operates entirely in the spectral domain and does not involve pitch-synchronous resynthesis (PSOLA), the pitch contour of the original recording is left unchanged.

To account for the small discrepancy between the programmed and realised formant shift that arises from the Burg tracker operating on the resynthesised signal, an iterative correction procedure is applied. After each resynthesis, the geometric mean of F1–F4 is measured; if the absolute difference between the measured and target value exceeds 10 Hz, the scaling ratio is updated proportionally as $r \leftarrow r \cdot (\text{target} / \text{measured})$. This repeats up to a maximum of twelve iterations; convergence is typically achieved within two to three iterations.

**Step 2 — $f_0$ mean and $f_0$ SD.** $f_0$ mean and $f_0$ SD are manipulated jointly in a second step, applied to the formant-shifted intermediate. An autocorrelation-based pitch estimate is computed from this intermediate, yielding its actual $f_0$ mean ($\mu_\text{src}$) and $f_0$ SD ($\sigma_\text{src}$). An affine transform is then applied to every voiced frame:

$$f_0^\prime(t) = a + b \cdot f_0(t)$$

where the slope $b = \sigma_\text{target} / \sigma_\text{src}$ scales the pitch distribution width, and the intercept $a = \mu_\text{target} - \mu_\text{src} \cdot b$ shifts its centre. The modified pitch object is converted to a PitchTier, inserted into a Praat Manipulation object, and the final sound is obtained via overlap-add PSOLA resynthesis.

Because PSOLA resynthesis introduces a small but systematic discrepancy between the programmed and realised pitch SD, arising from differences between the fixed-timestep pitch analysis grid and the pitch-period-based PitchTier representation, an iterative correction procedure is applied. After each resynthesis, the output is re-analysed; if the absolute difference between the measured and target SD exceeds 0.5 Hz, the slope is updated multiplicatively as $b \leftarrow b \cdot (\sigma_\text{target} / \sigma_\text{measured})$, with the intercept recomputed from the fixed source mean. This repeats up to a maximum of five iterations; convergence is typically achieved within two to three iterations.

**Verification.** All eight output files are re-analysed independently after saving using the same pitch and formant analysis settings as the baseline (5500 Hz ceiling throughout, consistent with synthesis). The geometric mean of F1–F4 is used as the formant frequency metric, consistent with the population norm derivation. The realised $f_0$ mean, $f_0$ SD, and formant frequencies of each stimulus will be reported in the manuscript. The full script is available at \colorbox{BurntOrange}{ADD-URL}.

\newpage

# simulation-based power analysis

## Packages

All packages are available from CRAN. The analysis uses the `tidyverse` ecosystem [@tidyversecit] for data manipulation and visualisation, `lmerTest` [@lmerTestcit] for LMMs with Satterthwaite degrees of freedom and $p$-values, `emmeans` [@emmeanscit] for marginal contrasts and confidence intervals, `effectsize` [@effectsizecit] for partial $\omega^2$ estimates, `furrr` [@furrrcit] for parallel Monte Carlo sampling, `brms` [@brmscit1; @brmscit2] for Bayesian LMMs via Stan, `bayestestR` [@bayestestRcit] for ROPE-based equivalence testing, and `posterior` [@posteriorcit] for summarising and diagnosing posterior distributions. Visualisation uses `ggdist` [@ggdistcit1; @ggdistcit2], `tidyquant` [@tidyquantcit], `ggpubr` [@ggpubrcit], and `tinytable` [@tinytablecit] for publication-quality tables. The Bayesian models are compiled and sampled via `cmdstanr` [@cmdstanrcit], which provides an R interface to *CmdStan* and is used as the backend for `brms`.

```{r}
#| label: packages
#| cache: false

library(tidyverse)    # Data manipulation and visualisation
library(lmerTest)     # LMMs with Satterthwaite df and p-values
library(emmeans)      # Marginal contrasts and CIs
library(effectsize)   # Partial omega-squared
library(furrr)        # Parallel Monte Carlo via purrr
library(future)       # Parallel back-end for furrr
library(ggdist)       # Raincloud plot components
library(tidyquant)    # Colour palettes and themes
library(ggpubr)       # Multi-panel figure arrangement
library(scales)       # Axis formatting utilities
library(tinytable)    # Publication-quality tables (PDF-safe)
library(brms)         # Bayesian LMMs via Stan
library(bayestestR)   # ROPE and equivalence testing for Bayesian models
library(posterior)    # Posterior manipulation (brms dependency)
library(cmdstanr)     # Stan backend for brms (faster than rstan)
set_cmdstan_path()    # Locate CmdStan installation (required each session)
if (!dir.exists(cmdstan_path())) {
  stop("CmdStan not found. Run cmdstanr::install_cmdstan() first.")
}
```

## Global Parameters {#sec-parameters}

All key parameters are defined here. Changes propagate automatically throughout the document.

```{r}
#| label: parameters
#| cache: false

# ── Simulation scale ─────────────────────────────────────────────────────────
set.seed(2025)          # Global seed for reproducibility
n_pop        <- 10000   # Size of each simulated superpopulation
n_sim        <- 1000    # Monte Carlo iterations per sample size (frequentist)
n_sim_bayes  <- 1000    # brms simulations at target n
                           
sample_sizes <- seq(100, 300, by = 10)  # Sample sizes evaluated
target_n     <- 200     # Pre-specified target sample size

# ── Analysis parameters ───────────────────────────────────────────────────────
alpha    <- 0.05 # Significance level (frequentist detection)
ci_level <- 0.90 # CI level for equivalence tests (= 1 - 2*alpha)
eq_bound <- 150  # Equivalence bound (ms); justification in Section 2.3 

# ── Simulated effect sizes (ms) — H1 population ───────────────────────────────
# Main effects (H1: f0 SD, H2: f0 mean; formant frequencies exploratory)
eff_f0sd    <- 100 # f0 SD: expected mean difference (High vs. Low), ms
eff_f0mean  <-  75 # f0 mean: expected mean difference (High vs. Low), ms
eff_ffreq   <-  50 # Formant freq.: expected mean difference (High vs. Low), ms

# Interaction effects (exploratory only)
eff_f0sd_f0mean  <- 100  # f0 SD x f0 mean
eff_f0sd_ffreq   <- 100  # f0 SD x formant freq.
eff_f0mean_ffreq <-  50  # f0 mean x formant freq.
eff_triple       <- 120  # f0 SD x f0 mean x formant freq. (triple interaction)

# ── Data-generating model parameters (shared by both populations) ─────────────
baseline    <- 2500 # Baseline fixation time (ms; all predictors = Low)
residual_sd <- 1000 # Trial-level residual SD (ms)
y_min       <- 0    # Floor of fixation-time distribution (ms)
y_max       <- 5000 # Ceiling of fixation-time distribution (ms)

# ── brms ROPE range (same as frequentist equivalence bounds) ──────────────────
rope_range <- c(-eq_bound, eq_bound)
```

\newpage

## Equivalence Bounds: Justification and Pre-specification {#sec-bounds}

### Rationale for Equivalence Testing

Conventional null-hypothesis significance testing (NHST) cannot distinguish between a true null effect and an underpowered study. For a registered report, it is therefore essential to pre-specify a procedure that permits positive evidence for the absence of a meaningful effect. The two one-sided tests (TOST) procedure achieves this by testing whether an observed effect lies within pre-defined equivalence bounds $[-\Delta, +\Delta]$, or equivalently, whether the $(1 - 2\alpha)$ CI falls entirely within those bounds [@lakensEquivalenceTestsPractical2017].

### Defining the Smallest Effect Size of Interest (SESOI)

The equivalence bounds must be anchored to a *smallest effect size of interest* (SESOI): the minimum difference in fixation time that would be theoretically or practically meaningful. The two confirmatory hypotheses are associated with expected effects of `r eff_f0sd` ms ($f_0$ SD, H1) and `r eff_f0mean` ms ($f_0$ mean, H2). The exploratory formant frequencies parameter assumes an expected effect of `r eff_ffreq` ms (see @sec-popdata). Rather than defining the SESOI purely in terms of these predicted effects, we anchor it to the **precision limit of the design**: the smallest effect that a well-powered infant eye-tracking study of feasible size could realistically detect.

With a residual standard deviation of $\sigma \approx `r residual_sd`$ ms (consistent with published infant eye-tracking data) and $n = `r target_n`$ participants each contributing 4 observations per level of each factor, the approximate standard error of the marginal High $-$ Low contrast is:

$$SE \approx \sqrt{\frac{\sigma^2}{2n}} =
  \sqrt{\frac{`r residual_sd`^2}{2 \times `r target_n`}} \approx
  `r round(sqrt(residual_sd^2 / (2 * target_n)), 1)`\text{ ms}$$

For 80% equivalence power, the required bounds are:

$$\Delta_{80\%} \approx SE \times (z_{0.90} + z_{0.80}) =
  `r round(sqrt(residual_sd^2 / (2 * target_n)), 1)` \times 2.927 \approx
  `r round(sqrt(residual_sd^2 / (2 * target_n)) * 2.927, 0)`\text{ ms}$$

We set equivalence bounds at $\Delta = \pm`r eq_bound`$ ms (the rounded value closest to $\Delta_{80\%}$ that remains scientifically interpretable). An effect smaller than `r eq_bound` ms represents `r round(eq_bound / (y_max - y_min) * 100, 0)`% of the total fixation-time range (0–`r y_max` ms) and `r round(eq_bound / eff_f0sd * 100, 0)`% of the largest expected main effect ($f_0$ SD = `r eff_f0sd` ms). Such an effect would be undetectable by any practically feasible infant eye-tracking study and is therefore an appropriate threshold for inferring negligibility.

### Equivalence Power

The H$_0$ Monte Carlo simulation in @sec-mc confirms that, at $n = `r target_n`$ with bounds of $\pm`r eq_bound`$ ms, equivalence power reaches approximately 80%. This is an honest reflection of the precision constraints of the infant
eye-tracking paradigm: the high trial-level noise ($\sigma \approx `r residual_sd`$ ms) means that ruling out effects smaller than `r eq_bound` ms requires the full target sample. Equivalence power at smaller $n$ (e.g., $n = 160$) would be substantially lower (~70%), which is one motivation for the planned sample size to $n = `r target_n`$.

### Operationalisation

#### Frequentist equivalence test

The marginal pairwise contrast (High $-$ Low, averaged over all levels of the other two factors) is estimated using `emmeans` with Satterthwaite degrees of freedom. A `r ci_level * 100`% CI is computed. Equivalence is concluded if:

$$\text{Lower CL} > `r -eq_bound`\text{ ms} \;\;\text{and}\;\; \text{Upper CL} < `r eq_bound`\text{ ms}$$

Equivalence power is estimated from a dedicated H$_0$ superpopulation in which all acoustic effects are zero (see @sec-null), ensuring the estimate describes the correct conditional probability.

#### Bayesian ROPE

The same bounds define the ROPE for the Bayesian sensitivity analysis. Weakly informative priors place no strong prior mass near zero, so high ROPE percentages reflect genuine posterior evidence for equivalence. Following [@kruschkeDoingBayesianData2015], we report both the ROPE percentage and whether the `r ci_level * 100`% Highest Density Interval (HDI) [@kruschkeDoingBayesianData2015; @bayestestRcit] falls entirely within the ROPE (strong equivalence).

\newpage

## Simulated Population Data {#sec-popdata}

### H$_1$ Population: Non-Zero Acoustic Effects

Each participant observes all eight combinations of three acoustic factors, $f_0$ SD (Low/High), $f_0$ mean (Low/High), and formant frequencies (Low/High), yielding a 2×2×2 fully crossed within-subjects design. The outcome is total fixation time (ms), bounded to [0, 5000]. We simulate an H$_1$ superpopulation of $N = `r format(n_pop, big.mark = ",")`$ participants (×8 conditions = `r format(n_pop * 8, big.mark = ",")` rows) from which Monte Carlo samples are drawn to estimate **detection power**.

The data-generating model is:

$$
\begin{aligned}
Y_{ij} &= \mu + \beta_1 f_0\text{SD}_{j} + \beta_2 f_0\text{mean}_{j}
         + \beta_3 \text{formant}_{j}
         + \beta_{12}(f_0\text{SD} \times f_0\text{mean})_j \\
       &\quad + \beta_{13}(f_0\text{SD} \times \text{formant})_j
         + \beta_{23}(f_0\text{mean} \times \text{formant})_j
         + \beta_{123}(f_0\text{SD} \times f_0\text{mean} \times \text{formant})_j
         + \epsilon_{ij}
\end{aligned}
$$

where $\mu = `r baseline`$ ms, the $\beta$ coefficients correspond to the effect
sizes in @sec-parameters, and $\epsilon_{ij} \sim \mathcal{N}(0, \sigma^2)$,
truncated to $[`r y_min`, `r y_max`]$.

```{r}
#| label: pop-helper

# Helper: build a fully crossed superpopulation --------------------------------
make_population <- function(n, seed_offset,
                            b_f0sd, b_f0mean, b_ffreq,
                            b_f0sd_f0mean, b_f0sd_ffreq,
                            b_f0mean_ffreq, b_triple,
                            mu    = baseline,
                            sigma = residual_sd,
                            ymin  = y_min,
                            ymax  = y_max) {

  set.seed(2025 + seed_offset)

  conditions <- expand_grid(
    f0_sd   = c("Low", "High"),
    f0_mean = c("Low", "High"),
    ffreq   = c("Low", "High")
  )

  ids    <- str_c("P", str_pad(seq_len(n), width = nchar(n), pad = "0"))
  design <- expand_grid(ID = ids, conditions)

  design |>
    mutate(
      f0_sd_v   = if_else(f0_sd   == "High", 1L, 0L),
      f0_mean_v = if_else(f0_mean == "High", 1L, 0L),
      ffreq_v   = if_else(ffreq   == "High", 1L, 0L),
      mu_i =  mu
              + b_f0sd         * f0_sd_v
              + b_f0mean       * f0_mean_v
              + b_ffreq        * ffreq_v
              + b_f0sd_f0mean  * f0_sd_v  * f0_mean_v
              + b_f0sd_ffreq   * f0_sd_v  * ffreq_v
              + b_f0mean_ffreq * f0_mean_v * ffreq_v
              + b_triple       * f0_sd_v  * f0_mean_v * ffreq_v,
      fixation_time = round(rnorm(n(), mean = mu_i, sd = sigma)),
      fixation_time = pmin(pmax(fixation_time, ymin), ymax)
    ) |>
    mutate(
      f0_sd   = factor(f0_sd,   levels = c("Low", "High")),
      f0_mean = factor(f0_mean, levels = c("Low", "High")),
      ffreq   = factor(ffreq,   levels = c("Low", "High"))
    ) |>
    select(ID, f0_sd, f0_mean, ffreq, f0_sd_v, f0_mean_v, ffreq_v, fixation_time)
}
```

```{r}
#| label: simulate-h1

# H1 superpopulation (non-zero effects; used for detection power) --------------
h1_data <- make_population(
  n              = n_pop,
  seed_offset    = 0,
  b_f0sd         = eff_f0sd,
  b_f0mean       = eff_f0mean,
  b_ffreq        = eff_ffreq,
  b_f0sd_f0mean  = eff_f0sd_f0mean,
  b_f0sd_ffreq   = eff_f0sd_ffreq,
  b_f0mean_ffreq = eff_f0mean_ffreq,
  b_triple       = eff_triple
)
```

### H$_0$ Population: All Acoustic Effects Zero {#sec-null}

Detection power and equivalence power must be estimated from **separate** superpopulations. Detection power asks: given real effects, how often do we detect them? Equivalence power asks: given no effects, how often do we correctly conclude equivalence? The H$_0$ superpopulation is structurally identical to H$_1$ but with all acoustic effects set to zero.

```{r}
#| label: simulate-h0

# H0 superpopulation (all acoustic effects = 0; used for equivalence power) ---
h0_data <- make_population(
  n              = n_pop,
  seed_offset    = 1,   # different seed -> independent population
  b_f0sd         = 0,
  b_f0mean       = 0,
  b_ffreq        = 0,
  b_f0sd_f0mean  = 0,
  b_f0sd_ffreq   = 0,
  b_f0mean_ffreq = 0,
  b_triple       = 0
)
```

### Population-Level Model and Effect Sizes

```{r}
#| label: population-model

# Intercept-only random effects: appropriate at population scale and
# consistent with the signal-to-noise ratio of this design (see main text)
pop_mod <- lmer(
  fixation_time ~ f0_sd * f0_mean * ffreq + (1 | ID),
  data = h1_data
)

pop_omega <- omega_squared(pop_mod, partial = TRUE) |>
  rename(Effect = Parameter)
```

```{r}
#| label: tbl-population-effects
#| tbl-cap: >
#|   Population-level fixed effects from the LMM fitted to the full H$_1$
#|   superpopulation (*N* = 10,000). ANOVA table with Satterthwaite degrees of
#|   freedom, supplemented by partial $\omega^2$. Confirmatory effects (H1--H2)
#|   in the first two rows; formant frequencies (exploratory) in the third row;
#|   exploratory interactions follow.

anova(pop_mod) |>
  as.data.frame() |>
  rownames_to_column(var = "Effect") |>
  left_join(pop_omega |> select(Effect, Omega2_partial), by = "Effect") |>
  mutate(
    Hypothesis = case_when(
      Effect == "f0_sd"   ~ "H1",
      Effect == "f0_mean" ~ "H2",
      Effect == "ffreq"   ~ "Exploratory",
      TRUE                ~ "Exploratory"
    ),
    Effect = str_replace_all(Effect, "f0_sd",   "$f_0$ SD"),
    Effect = str_replace_all(Effect, "f0_mean", "$f_0$ mean"),
    Effect = str_replace_all(Effect, "ffreq",   "Formant freq."),
    Effect = str_replace_all(Effect, ":",       " $\\times$ "),
    DenDF         = round(DenDF, 1),
    `F value`     = round(`F value`, 2),
    Omega2_partial = round(Omega2_partial, 4)
  ) |>
  select(Hypothesis, Effect, `F value`, NumDF, DenDF, Omega2_partial) |>
  unite("$df$", NumDF:DenDF, sep = ", ") |>
  rename(
    "Hypothesis"    = Hypothesis,
    "Fixed effect"  = Effect,
    "$F$"           = `F value`,
    "$\\omega^2_p$" = Omega2_partial
  ) |>
  tt(notes = "\\textit{Note.} Partial $\\omega^2_p$ benchmarks \\cite{field2013}: 
     very small $< 0.01$; small $= 0.01$--$0.06$; medium $= 0.06$--$0.14$; 
     large $\\geq 0.14$.") |>
  style_tt(align = "llccc") |> 
  format_tt(escape = FALSE)
```

### Distribution of Fixation Times Across Conditions (H$_1$ Population)

```{r}
#| label: fig-raincloud
#| fig-cap: >
#|   Distribution of fixation times in the H$_1$ superpopulation as a function of
#|   $f_0$ SD (x-axis), $f_0$ mean (columns), and formant frequencies (rows). Each
#|   panel shows the density half-violin, jittered data points (2% random sample),
#|   and condition mean ± SE. Fixation times increase systematically with $f_0$ SD
#|   (the largest main effect), with additive contributions from $f_0$ mean and
#|   formant frequencies.
#| fig-height: 6.5

set.seed(1)
plot_data <- h1_data |> slice_sample(prop = 0.02)

label_f0mean <- c(
  "Low"  = "paste('Low ',  italic(f)[0], ' mean')",
  "High" = "paste('High ', italic(f)[0], ' mean')"
)
label_ffreq <- c(
  "Low"  = "'Low formant freq.'",
  "High" = "'High formant freq.'"
)

ggplot(h1_data, aes(x = f0_sd, y = fixation_time, fill = f0_sd)) +
  stat_halfeye(adjust = 0.5, justification = -0.3,
               .width = 0, point_colour = NA, alpha = 0.65) +
  geom_jitter(data = plot_data, aes(colour = f0_sd),
              width = 0.1, alpha = 0.3, size = 0.5) +
  stat_summary(fun = mean, geom = "point", size = 2.5, colour = "black",
               position = position_nudge(x = 0.22)) +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.1,
               colour = "black", position = position_nudge(x = 0.22)) +
  facet_grid(
    ffreq ~ f0_mean,
    labeller = labeller(
      f0_mean = as_labeller(label_f0mean, default = label_parsed),
      ffreq   = as_labeller(label_ffreq,  default = label_parsed)
    )
  ) +
  scale_fill_tq() +
  scale_colour_tq() +
  labs(
    x      = expression(italic(f)[0] ~ "SD"),
    y      = "Total fixation time (ms)",
    fill   = expression(italic(f)[0] ~ "SD"),
    colour = expression(italic(f)[0] ~ "SD")
  ) +
  theme_tq(base_size = 12) +
  theme(legend.position = "bottom")
```

\newpage

## Monte Carlo Power Analysis: Frequentist {#sec-mc}

### Simulation Strategy

Detection and equivalence power are estimated from two independent Monte Carlo
simulations:

- **Detection power** (H$_1$ population): `r n_sim` samples per candidate $n$ from `h1_data`. For each sample, the LMM ANOVA $p$-value is recorded for each main effect. Power = proportion of samples with $p < `r alpha`$.

- **Equivalence power** (H$_0$ population): `r n_sim` samples per candidate $n$ from  `h0_data`. For each sample, the marginal High $-$ Low contrast is estimated via `emmeans` (Satterthwaite df) with a `r ci_level * 100`% CI. Power = proportion of samples where the CI falls entirely within $[\text{-}`r eq_bound`$, $`r eq_bound`]$ ms.

Both loops cover $n$ = `r min(sample_sizes)` to `r max(sample_sizes)` (steps of 10) and run in parallel via `furrr`.

### Simulation Functions

```{r}
#| label: sim-functions

# Detection: p-values from LMM ANOVA (H1 data) --------------------------------
run_detection_sim <- function(dat, n_sample, n_sim, alpha = 0.05) {
  map_dfr(seq_len(n_sim), function(i) {
    ids  <- dat |> distinct(ID) |> slice_sample(n = n_sample) |> pull(ID)
    sdat <- dat |> filter(ID %in% ids)
    mod  <- suppressMessages(
      lmer(fixation_time ~ f0_sd * f0_mean * ffreq + (1 | ID), data = sdat)
    )
    av    <- anova(mod)
    terms <- c("f0_sd", "f0_mean", "ffreq")
    map_dfr(terms, function(trm) {
      tibble(
        sim      = i,
        n_sample = n_sample,
        term     = trm,
        p_detect = av[trm, "Pr(>F)"],
        detect   = av[trm, "Pr(>F)"] < alpha
      )
    })
  })
}

# Equivalence: 90% CIs from emmeans, check ROPE containment (H0 data) ---------
run_equivalence_sim <- function(dat, n_sample, n_sim,
                                ci_lev = 0.90, bound = eq_bound) {
  map_dfr(seq_len(n_sim), function(i) {
    ids  <- dat |> distinct(ID) |> slice_sample(n = n_sample) |> pull(ID)
    sdat <- dat |> filter(ID %in% ids)
    mod  <- suppressMessages(
      lmer(fixation_time ~ f0_sd * f0_mean * ffreq + (1 | ID), data = sdat)
    )
    terms <- c("f0_sd", "f0_mean", "ffreq")
    map_dfr(terms, function(trm) {
      em <- emmeans(mod, as.formula(paste0("~ ", trm)))
      ct <- pairs(em, reverse = TRUE)
      ci <- confint(ct, level = ci_lev)
      tibble(
        sim      = i,
        n_sample = n_sample,
        term     = trm,
        estimate = ci$estimate[1],
        ci_lo    = ci$lower.CL[1],
        ci_hi    = ci$upper.CL[1],
        sig      = ci$lower.CL[1] > 0 | ci$upper.CL[1] < 0,
        equiv    = ci$lower.CL[1] > -bound & ci$upper.CL[1] < bound
      )
    })
  })
}
```

### Run Detection Simulation (H$_1$ Population)

```{r}
#| label: run-detection
#| cache: true

plan(multisession)

detect_results <- map_dfr(
  sample_sizes,
  ~ run_detection_sim(
      dat      = h1_data,
      n_sample = .x,
      n_sim    = n_sim,
      alpha    = alpha
    )
)

plan(sequential)
```

### Run Equivalence Simulation (H$_0$ Population)

```{r}
#| label: run-equivalence
#| cache: true

plan(multisession)

equiv_results <- map_dfr(
  sample_sizes,
  ~ run_equivalence_sim(
      dat      = h0_data,
      n_sample = .x,
      n_sim    = n_sim,
      ci_lev   = ci_level,
      bound    = eq_bound
    )
)

plan(sequential)
```

### Summarise Power

```{r}
#| label: power-summary

term_labs <- c(
  "f0_sd"   = "italic(f)[0]~SD",
  "f0_mean" = "italic(f)[0]~mean",
  "ffreq"   = "Formant~freq."
)

detect_summ <- detect_results |>
  group_by(term, n_sample) |>
  summarise(power_detect = mean(detect, na.rm = TRUE), .groups = "drop")

equiv_summ <- equiv_results |>
  group_by(term, n_sample) |>
  summarise(power_equiv = mean(equiv, na.rm = TRUE), .groups = "drop")

power_summ <- detect_summ |>
  left_join(equiv_summ, by = c("term", "n_sample")) |>
  mutate(term = factor(term, levels = names(term_labs), labels = term_labs))

# Minimum n achieving > 95% detection power per effect
n_80_detect <- detect_summ |>
  filter(power_detect > 0.95) |>
  group_by(term) |>
  slice_min(n_sample) |>
  select(term, n_80_det = n_sample, pwr_det_80 = power_detect)

n_recommended        <- max(n_80_detect$n_80_det)
detect_at_target     <- detect_summ |> filter(n_sample == target_n)
equiv_at_target      <- equiv_summ  |> filter(n_sample == target_n)
```

### Power Curves

```{r}
#| label: cap-power-curves
#| include: false
cap_power_curves <- paste0(
  "Monte Carlo power curves for H1 ($f_0$ SD), H2 ($f_0$ mean), and formant ",
  "frequencies (exploratory; shown for transparency). ",
  "**Panel A:** Frequentist detection power ($p < .05$ in the LMM ANOVA), ",
  "estimated from the H$_1$ superpopulation. The dashed line marks the 95% target; ",
  "this threshold applies only to the confirmatory hypotheses (H1 and H2) --- ",
  "no power constraint applies to the exploratory formant frequencies parameter. ",
  "**Panel B:** Frequentist equivalence power (90% CI within ",
  "$\\pm ", eq_bound, "$ ms), estimated from the H$_0$ superpopulation (all ",
  "acoustic effects = 0). The dashed line marks the 80% equivalence power target ",
  "(see @sec-bounds). ",
  "The dotted vertical line marks $n = ", target_n, "$. ",
  "Points are coloured by whether power is above or at/below the panel-specific target."
)
```

```{r}
#| label: fig-power-curves
#| fig-cap: !expr cap_power_curves
#| fig-height: 5

power_threshold_detect <- 0.95
power_threshold_equiv  <- 0.80

make_power_plot <- function(data, y_var, title_str, threshold) {
  ggplot(data, aes(x = n_sample, y = .data[[y_var]], group = term)) +
    geom_line(linewidth = 0.5, colour = "grey40") +
    geom_point(aes(colour = .data[[y_var]] > threshold), size = 2) +
    geom_hline(yintercept = threshold,
               linetype = "dashed", colour = "red", linewidth = 0.6) +
    geom_vline(xintercept = target_n,
               linetype = "dotted", colour = "#2c3e50", linewidth = 0.6) +
    annotate("text", x = target_n + 2, y = 0.12,
             label = paste0("n = ", target_n),
             hjust = 0, colour = "#2c3e50", size = 3) +
    facet_wrap(
      ~ term, nrow = 1,
      labeller = as_labeller(
        setNames(levels(data$term), levels(data$term)),
        default = label_parsed
      )
    ) +
    scale_colour_tq(
      labels = c("FALSE" = "At or below target", "TRUE" = "Above target"),
      name   = "Power"
    ) +
    scale_y_continuous(labels = percent_format(accuracy = 1), limits = c(0, 1)) +
    labs(title = title_str, x = "Sample size (n)", y = "Estimated power") +
    theme_tq(base_size = 11) +
    theme(legend.position = "bottom")
}

ggarrange(
  make_power_plot(
    power_summ, "power_detect",
    "A  Detection power (frequentist, p < .05) \u2014 H\u2081 population",
    threshold = power_threshold_detect
  ),
  make_power_plot(
    power_summ, "power_equiv",
    paste0("B  Equivalence power (90% CI within \u00b1",
           eq_bound, " ms) \u2014 H\u2080 population"),
    threshold = power_threshold_equiv
  ),
  nrow = 2, common.legend = TRUE, legend = "bottom"
)
```

### Distribution of Contrast Estimates at Target Sample Size

```{r}
#| label: cap-contrast-dists
#| include: false
cap_contrast_dists <- paste0(
  "Sampling distributions of the marginal High $-$ Low contrast (ms) across ",
  n_sim, " Monte Carlo samples at $n = ", target_n, "$. ",
  "**Panel A (H$_1$ population):** Under real effects. Distributions are centred ",
  "near the true effects; the grey band marks the equivalence bounds ",
  "($\\pm ", eq_bound, "$ ms). Filled bars show the small fraction of samples in ",
  "which the CI nevertheless fell within the bounds. ",
  "**Panel B (H$_0$ population):** Under a true null. Distributions are centred ",
  "near zero. Filled (orange) bars show simulations where the 90% CI falls ",
  "entirely within $\\pm ", eq_bound, "$ ms (correct equivalence); grey bars are ",
  "inconclusive."
)
```

```{r}
#| label: fig-contrast-dists
#| fig-cap: !expr cap_contrast_dists
#| fig-height: 5

term_factor <- function(x) {
  factor(x, levels = names(term_labs), labels = term_labs)
}

# Use equivalence simulation output for H1 (already has estimate + CI)
set.seed(42)
h1_ci_sample <- run_equivalence_sim(
  dat      = h1_data,
  n_sample = target_n,
  n_sim    = 200,        # lighter subsample for plotting only
  ci_lev   = ci_level,
  bound    = eq_bound
) |> mutate(term_lab = term_factor(term))

h0_at_target <- equiv_results |>
  filter(n_sample == target_n) |>
  mutate(term_lab = term_factor(term))

make_dist_plot <- function(dat, title_str) {
  dat <- dat |>
    mutate(
      outcome = case_when(
        equiv            ~ "Equivalent",
        sig & !equiv     ~ "Significant, not equivalent",
        TRUE             ~ "Inconclusive"
      ),
      outcome = factor(outcome,
                       levels = c("Significant, not equivalent",
                                  "Equivalent",
                                  "Inconclusive"))
    )
  ggplot(dat, aes(x = estimate, fill = outcome)) +
    annotate("rect", xmin = -eq_bound, xmax = eq_bound,
             ymin = 0, ymax = Inf, fill = "grey85", alpha = 0.5) +
    geom_vline(xintercept = c(-eq_bound, eq_bound),
               linetype = "dashed", colour = "grey40", linewidth = 0.6) +
    geom_histogram(binwidth = 10, alpha = 0.85, colour = NA) +
    annotate("text", x = 0, y = Inf, vjust = 1.5,
             label = paste0("\u00b1", eq_bound, " ms"),
             fontface = "italic", colour = "grey35", size = 3) +
    facet_wrap(
      ~ term_lab, nrow = 1,
      labeller = as_labeller(
        setNames(levels(dat$term_lab), levels(dat$term_lab)),
        default = label_parsed
      )
    ) +
    scale_fill_manual(
      values = c(
        "Significant, not equivalent" = "#2ecc71",
        "Equivalent"                  = "#D55E00",
        "Inconclusive"                = "grey65"
      ),
      name = NULL
    ) +
    scale_x_continuous(breaks = pretty_breaks(n = 6)) +
    labs(title = title_str,
         x = "Estimated contrast: High \u2212 Low (ms)",
         y = "Frequency") +
    theme_tq(base_size = 11) +
    theme(legend.position = "bottom")
}

ggarrange(
  make_dist_plot(h1_ci_sample,
                 "A  H\u2081 population (real effects present)"),
  make_dist_plot(h0_at_target,
                 "B  H\u2080 population (all effects = 0)"),
  nrow = 2, common.legend = TRUE, legend = "bottom"
)
```

### Sample Size Summary

```{r}
#| include: false
cap_sample_size <- paste0(
  "Power summary at the target sample size ($n = ", target_n, "$). ",
  "Detection power is from H$_1$ simulations; equivalence power from ",
  "H$_0$ simulations. Equivalence power is intentionally modest given ",
  "the high trial-level noise of this design (see @sec-bounds for full discussion)."
)
```

```{r}
#| label: tbl-sample-size
#| tbl-cap: !expr cap_sample_size

detect_at_target |>
  left_join(equiv_at_target, by = c("term", "n_sample")) |>
  left_join(n_80_detect,     by = "term") |>
  arrange(factor(term, levels = c("f0_sd", "f0_mean", "ffreq"))) |>
  mutate(
    Effect = case_when(
      term == "f0_sd"   ~ "$f_0$ SD (H1)",
      term == "f0_mean" ~ "$f_0$ mean (H2)",
      term == "ffreq"   ~ "Formant freq. (Exploratory)"
    ),
    `Expected effect` = case_when(
      term == "f0_sd"   ~ paste0(eff_f0sd,    " ms"),
      term == "f0_mean" ~ paste0(eff_f0mean,  " ms"),
      term == "ffreq"   ~ paste0(eff_ffreq,   " ms")
    ),
    `Detection power`  = paste0(round(power_detect * 100, 1), "\\%"),
    `Equiv. power`     = paste0(round(power_equiv  * 100, 1), "\\%"),
    `Min $n$ (95\\% det.)` = n_80_det
  ) |>
  select(Effect, `Expected effect`, `Detection power`,
         `Min $n$ (95\\% det.)`, `Equiv. power`) |>
  tt(notes = paste0(
       "\\textit{Note.} Detection power: $p < .05$, from H$_1$ simulations at
       $n = ", target_n, "$. Target: $\\geq$95\\% for confirmatory hypotheses ",
       "(H1 and H2); formant frequencies are exploratory (no power constraint). ",
       "Equivalence power: 90\\% CI within $\\pm ",
       eq_bound, "$ ms, from H$_0$ simulations at $n = ", target_n,
       "$. Both based on ", n_sim,
       " Monte Carlo samples per candidate $n$."),
     width = c(0.30, 0.18, 0.18, 0.18, 0.16)) |>
  style_tt(align = "lcccc") |>
  format_tt(escape = FALSE)
```

The simulation confirms that a sample of **$n$ = `r n_recommended`** achieves $> 95\%$ detection power for both confirmatory main effects (H1: $f_0$ SD; H2: $f_0$ mean), and that the pre-specified target of $n$ = `r target_n` further ensures approximately 80% equivalence power at bounds of $\pm`r eq_bound`$ ms (see @sec-bounds). Formant frequencies are treated as exploratory, so no detection power threshold applies to that parameter. Both detection and equivalence considerations therefore motivate the target of $n$ = `r target_n`.

\newpage

## Bayesian Sensitivity Analysis: brms + ROPE {#sec-bayes}

### Rationale and Scope

The Bayesian analysis is a secondary robustness check. Rather than Bayes factors, which require bridge sampling and can be numerically unstable for complex LMMs,
we apply the ROPE procedure from `bayestestR` [@bayestestRcit] to posteriors from `brms` models. Two sets of `r n_sim_bayes` models are fitted at $n = `r target_n`$, mirroring the frequentist structure:

- **H$_1$ models**: data from `h1_data`. Posteriors should lie far from the ROPE, confirming sensitivity.
- **H$_0$ models**: data from `h0_data`. ROPE percentages should be high, quantifying Bayesian equivalence power.

## Prior Specification {#sec-priors}

We use **sum contrast coding** (Low = −0.5; High = +0.5) so that each main-effect coefficient equals the marginal High $-$ Low difference, directly comparable to the `emmeans` marginal contrast. Priors are weakly informative:

```{r}
#| label: tbl-priors
#| tbl-cap: Prior specification for Bayesian LMMs.

tibble(
  `Parameter class` = c(
    "Intercept",
    "Main effects and interactions",
    "Residual SD ($\\sigma$)",
    "Random-effect SD"
  ),
  Prior = c(
    "$\\mathcal{N}(2500,\\; 500^2)$",
    "$\\mathcal{N}(0,\\; 200^2)$",
    "Half-$\\mathcal{N}(0,\\; 500^2)$",
    "Half-$\\mathcal{N}(0,\\; 500^2)$"
  ),
  Rationale = c(
    "Grand mean; $\\pm$1 SD spans plausible range",
    "Allows effects up to $\\pm$400 ms; flat over realistic range",
    "Consistent with $\\sigma \\approx 1000$ ms in the DGM",
    "Weakly informative for participant variability"
  )
) |>
  tt(align = "lll", width = c(0.25, 0.30, 0.40)) |>
  format_tt(escape = FALSE)
```

```{r}
#| label: priors

brms_priors <- c(
  prior(normal(2500, 500), class = Intercept),
  prior(normal(0, 200),    class = b),
  prior(normal(0, 500),    class = sigma),
  prior(normal(0, 500),    class = sd)
)
```

### Simulation Function

> **Reproducibility note.** Each model uses seed `base_seed + i` to ensure
> independent, reproducible chains across simulations.

```{r}
#| label: brms-sim-function

run_bayes_sim <- function(dat, n_sample, n_sim_b, priors,
                          chains = 2, iter = 2000, warmup = 1000,
                          bound = eq_bound, ci_lev = ci_level,
                          base_seed = 9999) {

  map_dfr(seq_len(n_sim_b), function(i) {

    ids  <- dat |> distinct(ID) |> slice_sample(n = n_sample) |> pull(ID)
    sdat <- dat |> filter(ID %in% ids) |>
      mutate(
        f0_sd_c   = if_else(f0_sd   == "High", 0.5, -0.5),
        f0_mean_c = if_else(f0_mean == "High", 0.5, -0.5),
        ffreq_c   = if_else(ffreq   == "High", 0.5, -0.5)
      )

    fit <- brm(
      fixation_time ~ f0_sd_c * f0_mean_c * ffreq_c + (1 | ID),
      data    = sdat,
      family  = gaussian(),
      prior   = priors,
      chains  = chains,
      iter    = iter,
      warmup  = warmup,
      cores   = chains,
      seed    = base_seed + i,
      refresh = 0,
      silent  = 2,
      backend = "cmdstanr"   # change to "rstan" if cmdstanr is not installed
    )

    eq_res <- equivalence_test(
      fit,
      range = c(-bound, bound),
      ci    = ci_lev
    ) |>
      filter(Parameter %in% c("b_f0_sd_c", "b_f0_mean_c", "b_ffreq_c"))

    post <- as_draws_df(fit)

    tibble(
      sim            = i,
      n_sample       = n_sample,
      term           = c("f0_sd", "f0_mean", "ffreq"),
      posterior_mean = c(mean(post$b_f0_sd_c),
                         mean(post$b_f0_mean_c),
                         mean(post$b_ffreq_c)),
      posterior_sd   = c(sd(post$b_f0_sd_c),
                         sd(post$b_f0_mean_c),
                         sd(post$b_ffreq_c)),
      rope_pct       = eq_res$ROPE_Percentage,
      rope_equiv     = eq_res$ROPE_Equivalence,
      hdi_low        = eq_res$HDI_low,
      hdi_high       = eq_res$HDI_high
    )
  })
}
```

### Run Bayesian Simulations

```{r}
#| label: run-bayes-h1
#| cache: true

bayes_h1 <- run_bayes_sim(
  dat       = h1_data,
  n_sample  = target_n,
  n_sim_b   = n_sim_bayes,
  priors    = brms_priors,
  base_seed = 1000
)
```

```{r}
#| label: run-bayes-h0
#| cache: true

bayes_h0 <- run_bayes_sim(
  dat       = h0_data,
  n_sample  = target_n,
  n_sim_b   = n_sim_bayes,
  priors    = brms_priors,
  base_seed = 2000
)
```

### Results: ROPE Percentages and Posterior Summaries

```{r}
#| include: false

cap_bayes_rope_tbl <- paste0(
  "Bayesian ROPE analysis across ", n_sim_bayes, 
  " simulations per population at $n = ", target_n, 
  "$. Under H$_1$ (real effects), ROPE percentages should be low ",
  "(posteriors outside the ROPE). Under H$_0$ (null effects), ",
  "ROPE percentages should be high (posteriors within the ROPE)."
)
```

```{r}
#| label: tbl-bayes-rope
#| tbl-cap: !expr cap_bayes_rope_tbl

format_bayes_row <- function(dat, pop_label) {
  dat |>
    group_by(term) |>
    summarise(
      Population = pop_label,
      Effect = case_when(
        first(term) == "f0_sd"   ~ "$f_0$ SD (H1)",
        first(term) == "f0_mean" ~ "$f_0$ mean (H2)",
        first(term) == "ffreq"   ~ "Formant freq. (Exploratory)"
      ),
      `Post. mean (SD)` = paste0(
        round(mean(posterior_mean), 1), " (",
        round(mean(posterior_sd),   1), ")"
      ),
      `Mean ROPE \\%` = paste0(
        round(mean(rope_pct, na.rm = TRUE) * 100, 1), "\\%"
      ),
      `Prop. HDI in ROPE` = paste0(
        round(mean(rope_equiv == "Accepted", na.rm = TRUE) * 100, 1), "\\%"
      ),
      .groups = "drop"
    ) |>
    select(-term)
}

bind_rows(
  format_bayes_row(bayes_h1, "H$_1$ (effects present)"),
  format_bayes_row(bayes_h0, "H$_0$ (effects = 0)")
) |>
  arrange(Effect, Population) |>
  tt(notes = paste0("\\textit{Note.} ROPE $= [\\pm ", eq_bound, "$ ms]. ",
       "ROPE \\% = proportion of posterior within ROPE. ",
       "HDI in ROPE = entire ", ci_level * 100,
       "\\% HDI within ROPE (strong equivalence). ",
       "Based on $n_{\\text{sim}} = ", n_sim_bayes,
       "$ simulations."),
     width = c(0.22, 0.24, 0.20, 0.17, 0.17)) |>
  style_tt(align = "llccc") |>
  format_tt(escape = FALSE)
```

### Posterior Distributions and ROPE Percentages

```{r}
#| label: cap-bayes-rope
#| include: false
cap_bayes_rope <- paste0(
  "Bayesian posterior estimates and ROPE percentages across ",
  n_sim_bayes, " simulations at $n = ", target_n, "$, under both populations. ",
  "**Left column:** Posterior mean estimates (High $-$ Low, ms). The grey shaded ",
  "region marks the ROPE ($\\pm ", eq_bound, "$ ms). Under H$_1$, posteriors should ",
  "lie well outside the ROPE; under H$_0$, they should cluster near zero. ",
  "**Right column:** ROPE percentages. The dashed line marks 50%. High ROPE % under ",
  "H$_0$ and low ROPE % under H$_1$ confirms that the model discriminates correctly."
)
```

```{r}
#| label: fig-bayes-rope
#| fig-cap: !expr cap_bayes_rope
#| fig-height: 8

prep_bayes <- function(dat, label) {
  dat |> mutate(
    Population = label,
    term_lab   = factor(term, levels = names(term_labs), labels = term_labs)
  )
}

bayes_combined <- bind_rows(
  prep_bayes(bayes_h1, "H\u2081 (effects present)"),
  prep_bayes(bayes_h0, "H\u2080 (effects = 0)")
)

p_post <- ggplot(bayes_combined,
                 aes(x = posterior_mean, fill = Population)) +
  annotate("rect", xmin = -eq_bound, xmax = eq_bound,
           ymin = 0, ymax = Inf, fill = "grey85", alpha = 0.5) +
  geom_vline(xintercept = c(-eq_bound, eq_bound),
             linetype = "dashed", colour = "grey40") +
  geom_histogram(bins = 15, colour = "white", alpha = 0.8,
                 position = "identity") +
  facet_wrap(
    ~ term_lab, nrow = 3,
    labeller = as_labeller(
      setNames(levels(bayes_combined$term_lab),
               levels(bayes_combined$term_lab)),
      default = label_parsed
    ),
    scales = "free_x"
  ) +
  scale_fill_tq() +
  labs(title = "Posterior mean estimates",
       x = "Posterior mean: High \u2212 Low (ms)",
       y = "Count", fill = NULL) +
  theme_tq(base_size = 11) +
  theme(legend.position = "bottom")

p_rope_pct <- ggplot(bayes_combined,
                     aes(x = rope_pct * 100, fill = Population)) +
  geom_histogram(bins = 15, colour = "white", alpha = 0.8,
                 position = "identity") +
  geom_vline(xintercept = 50, linetype = "dashed", colour = "red") +
  facet_wrap(
    ~ term_lab, nrow = 3,
    labeller = as_labeller(
      setNames(levels(bayes_combined$term_lab),
               levels(bayes_combined$term_lab)),
      default = label_parsed
    )
  ) +
  scale_fill_tq() +
  scale_x_continuous(labels = function(x) paste0(x, "%")) +
  labs(title = "ROPE percentages",
       x = paste0("% of posterior within \u00b1", eq_bound, " ms"),
       y = "Count", fill = NULL) +
  theme_tq(base_size = 11) +
  theme(legend.position = "bottom")

ggarrange(p_post, p_rope_pct,
          labels = "AUTO", ncol = 2,
          common.legend = TRUE, legend = "bottom")
```

\newpage

## Overall Summary {#sec-summary}

```{r}
#| include: false

cap_tbl_final_summary <- paste0(
  "Combined frequentist and Bayesian power summary at the pre-specified target ",
  "sample size ($n = ", target_n, "$). Detection and equivalence power are from ",
  "Monte Carlo simulations (H$_1$ and H$_0$ superpopulations respectively). ",
  "ROPE percentages are means across ", n_sim_bayes, " Bayesian LMMs fitted via ",
  "\\texttt{brms} at $n = ", target_n, "$. ",
  "The study meets the $\\geq95\\$% detection power target for both confirmatory ",
  "hypotheses (H1 and H2). Formant frequencies are exploratory and carry no ",
  "power constraint. Equivalence power is modest but reflects the precision ",
  "limits of the infant eye-tracking paradigm (see @sec-bounds)."
)
```

```{r}
#| label: tbl-final-summary
#| tbl-cap: !expr cap_tbl_final_summary

detect_at_target |>
  left_join(equiv_at_target, by = c("term", "n_sample")) |>
  left_join(
    bayes_h1 |>
      group_by(term) |>
      summarise(`ROPE\\% (H$_1$)` = paste0(
                  round(mean(rope_pct, na.rm = TRUE) * 100, 1), "\\%"),
                .groups = "drop"),
    by = "term"
  ) |>
  left_join(
    bayes_h0 |>
      group_by(term) |>
      summarise(`ROPE\\% (H$_0$)` = paste0(
                  round(mean(rope_pct, na.rm = TRUE) * 100, 1), "\\%"),
                .groups = "drop"),
    by = "term"
  ) |>
  arrange(factor(term, levels = c("f0_sd", "f0_mean", "ffreq"))) |>
  mutate(
    Effect = case_when(
      term == "f0_sd"   ~ "$f_0$ SD (H1)",
      term == "f0_mean" ~ "$f_0$ mean (H2)",
      term == "ffreq"   ~ "Formant freq. (Exploratory)"
    ),
    `Exp. effect` = case_when(
      term == "f0_sd"   ~ paste0(eff_f0sd,    " ms"),
      term == "f0_mean" ~ paste0(eff_f0mean,  " ms"),
      term == "ffreq"   ~ paste0(eff_ffreq,   " ms")
    ),
    `Det. power`   = paste0(round(power_detect * 100, 1), "\\%"),
    `Equiv. power` = paste0(round(power_equiv  * 100, 1), "\\%")
  ) |>
  select(Effect, `Exp. effect`, `Det. power`, `Equiv. power`,
         `ROPE\\% (H$_1$)`, `ROPE\\% (H$_0$)`) |>
  tt(notes = paste0(
       "\\textit{Note.} Equivalence bounds: $\\pm ", eq_bound, "$ ms ",
       "(see \\hyperref[sec-bounds]{Section~2.3}). ",
       "Det. power: frequentist LMM, $p < .05$, H$_1$ population; ",
       "target $\\geq$95\\% for H1 and H2 (no constraint for exploratory ",
       "formant frequencies). ",
       "Equiv. power: 90\\% CI within equivalence bounds, H$_0$ population. ",
       "ROPE \\%: mean proportion of posterior within $\\pm ", eq_bound,
       "$ ms across ", n_sim_bayes, " \\texttt{brms} simulations; H$_1$ ",
       "values should be low (posteriors outside ROPE when real effects exist) ",
       "and H$_0$ values should be high (posteriors near zero under null). ",
       "See \\hyperref[sec-bayes]{Section~2.6} for full Bayesian results ",
       "including HDI diagnostics."),
     width = c(0.27, 0.12, 0.14, 0.14, 0.16, 0.17)) |>
  group_tt(j = list("Frequentist" = 3:4, "Bayesian ROPE" = 5:6)) |>
  style_tt(align = "lccccc") |>
  format_tt(escape = FALSE)
```

The simulation confirms that:

- At **$n$ = `r target_n`**, detection power exceeds 95% for both confirmatory main effects (H1: $f_0$ SD; H2: $f_0$ mean) under the assumed population effect sizes. Formant frequencies are treated as exploratory and carry no detection power constraint.
- **Equivalence bounds** are set at $\pm`r eq_bound`$ ms, anchored to the precision limit of the design: the smallest effect detectable by a practically feasible infant eye-tracking study of this type, given $\sigma \approx `r residual_sd`$ ms. This corresponds to `r round(eq_bound / (y_max - y_min) * 100, 0)`% of the total fixation-time range and `r round(eq_bound / eff_f0sd * 100, 0)`% of the largest expected main effect [@simonsohnSmallTelescopes2015; @lakensEquivalenceTestingPsychological2018].
- **Equivalence power** at $n$ = `r target_n` is approximately `r paste0(round(mean(equiv_at_target$power_equiv) * 100, 0), "%")` on average, meeting the 80% target.
- The **frequentist equivalence test** generalises TOST to LMM fixed effects via model-based `emmeans` CIs; detection and equivalence power are estimated from separate superpopulations as required for correct interpretation [@lakensEquivalenceTestsPractical2017].
- The **Bayesian ROPE analysis** uses `brms` with weakly informative priors and `bayestestR`'s `equivalence_test()` [@bayestestRcit]. ROPE percentages are summarised alongside frequentist results in the table above; H$_1$ values confirm sensitivity (posteriors outside the ROPE when real effects are present) and H$_0$ values confirm specificity (posteriors inside the ROPE under the null). Full posterior distributions and HDI diagnostics are in @sec-bayes.
- **Interaction effects** are not powered at this sample size and are treated as exploratory throughout.

\newpage

# Session Information {.unnumbered}

```{r}
#| label: session-info
#| cache: false

pander::pander(sessionInfo(), locale = FALSE)
```

# References
